%----------
%   WARNING
%----------

% 
% This Guide contains Library recommendations based mainly on APA and IEEE styles (https://uc3m.libguides.com/en/thesis/), but you must always follow the guidelines of your thesis Tutor and the rules and regulations of the Doctoral School.

%----------
%	DOCUMENT SETTINGS
%----------

\documentclass[12pt]{report} % font: 12pt

% MÁRGENES: 2,5 cm top an bottom; 3 cm left and right
\usepackage[
a4paper,
vmargin=2.5cm,
hmargin=3cm
]{geometry}

% Paragraph Spacing and Line Spacing: Narrow (6 pt / 1.15 spacing) or Moderate (6 pt / 1.5 spacing)
\renewcommand{\baselinestretch}{1.15}
\parskip=6pt

% PDF/A -- Important for its inclusion in e-Archive. PDF/A is the optimal format for preservation and for the generation of metadata: http://uc3m.libguides.com/ld.php?content_id=31389625. 

% In the template we include the file OUTPUT.XMPDATA. You can download that file and include the metadata that will be incorporated into the PDF file when you compile the memoria.tex file. Then upload it back to your project.   
\usepackage[a-1b]{pdfx}

% LINKS
\usepackage{hyperref}
\hypersetup{colorlinks=true,
	linkcolor=black, % links to parts of the document (e.g. index) in black
	urlcolor=blue} % links to resources outside the document in blue

% MATH EXPRESSIONS
\usepackage{amsmath,amssymb,amsfonts,amsthm}

% Character encoding
\usepackage{txfonts} 
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% English settings
\usepackage[english]{babel} 
\usepackage[babel, english=american]{csquotes}
\AtBeginEnvironment{quote}{\small}

% Footer settings
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\rfoot{\thepage}
\fancypagestyle{plain}{\pagestyle{fancy}}

% DESIGN OF THE TITLES of the parts of the work (chapters and epigraphs or sub-chapters)
\usepackage{titlesec}
\usepackage{titletoc}
\titleformat{\chapter}[block]
{\large\bfseries\filcenter}
{\thechapter.}
{5pt}
{\MakeUppercase}
{}
\titlespacing{\chapter}{0pt}{0pt}{*3}
\titlecontents{chapter}
[0pt]                                               
{}
{\contentsmargin{0pt}\thecontentslabel.\enspace\uppercase}
{\contentsmargin{0pt}\uppercase}                        
{\titlerule*[.7pc]{.}\contentspage}                 

\titleformat{\section}
{\bfseries}
{\thesection.}
{5pt}
{}
\titlecontents{section}
[5pt]                                               
{}
{\contentsmargin{0pt}\thecontentslabel.\enspace}
{\contentsmargin{0pt}}
{\titlerule*[.7pc]{.}\contentspage}

\titleformat{\subsection}
{\normalsize\bfseries}
{\thesubsection.}
{5pt}
{}
\titlecontents{subsection}
[10pt]                                               
{}
{\contentsmargin{0pt}                          
	\thecontentslabel.\enspace}
{\contentsmargin{0pt}}                        
{\titlerule*[.7pc]{.}\contentspage}  

% Footnotes
\usepackage{chngcntr}
\counterwithout{footnote}{chapter}

% FIGURES
\usepackage{graphicx}
\graphicspath{{imagenes/}} % Images folder

%REFERENCES 

% IEEE bibliography setup
\usepackage[backend=biber, style=ieee, isbn=false,sortcites, maxbibnames=6, minbibnames=1]{biblatex} % Setting for IEEE citation style, recommended for engineering. "maxbibnames" indicates that from 6 authors truncate the list in the first one (minbibnames) and add "et al." as used in the IEEE style.

\addbibresource{referencias.bib}  % The references.bib file in which the bibliography used should be

%-------------
%	DOCUMENT
%-------------

\begin{document}
\pagenumbering{roman} % Roman numerals are used in the numbering of the pages preceding the body of the work.
%----------
%	COVER
%----------	
\begin{titlepage}
	%\begin{sffamily}
	\begin{center}
		\begin{huge}
			Labeling Data by using an Unsupervised Decision Support System in Order to be able to Identify Driving Patterns and Get a Coefficient that could be use to Calculate the Premium for an Insurance Car Policy\\			
			\bigskip
			by\\
			\bigskip
			José de Jesús Martínez Cámara\\
		\end{huge}
	    \vspace{2cm}	
	    \begin{large}
            A dissertation submitted by in partial fulfillment of the requirements for the degree of Doctor of Science in\\
            \bigskip
            Data Science\\
		    \vspace{2cm}
		    INFOTEC\\
		    \vspace{2cm}
		    Advisor(s):\\
		    \bigskip
		    Hamurabi Gamboa\\
		    Eduardo Sanchez (External)\\
		    \bigskip
		    Tutor:\\
		    \bigskip
		    Hamurabi Gamboa\\
		    \bigskip
		    Jun\\
		 \end{Large}
		 
	\end{center}
	\end{titlepage}
	
%----------
%	LICENCIA CREATIVE COMMONS
%----------	
	% IF OUR WORK IS TO BE PUBLISHED UNDER A CREATIVE COMMONS LICENSE, INCLUDE THESE LINES. IS THE RECOMMENDED OPTION.

%----------
%	DEDICATION
%----------	
% If you do not wish to add a dedication to your thesis, do not include this page.
\newpage
\thispagestyle{empty}
\begin{flushright}
Add your dedication here.
\end{flushright}

%----------
%	ACKNOWLEDGEMENTS
%----------	
% If you do not wish any acknowledgements to your thesis, do not include this page.
\chapter*{Acknowledgements}
\thispagestyle{empty}
Add acknowledgements here. 

%----------
%	PUBLISHED AND SUBMITTED CONTENT
%----------	
\chapter*{Published and submitted content}
\thispagestyle{empty}
\begin{itemize}
    \item Include a bibliography of articles or other contributions you have (co)authored that are included as part of the thesis and that
    \begin{itemize}
        \item have been published (describe your role; citations must include DOIs or publisher URLs if available electronically);  
        \item have been submitted for publication (describe your role; citations must include URLs if available electronically);
        \item have been submitted for a degree or any other qualification at UC3M or any other institution (describe degree or qualification, institution, and year of completion).
    \end{itemize}
    \item For each item 
    \begin{itemize}
        \item State whether the item is partly or wholly included in the Thesis;
        \item Indicate the chapter or chapters where material from this item is included;
        \item Optional statement: “The inclusion in the thesis of material from this source is specified in a footnote to each chapter where an inclusion occurs.”
        \item Choose one of the following statements:
        \begin{itemize}
            \item The material from this source included in this thesis is not singled out with typographic means and references.
            \item Whenever material from this source is included in this thesis, it is singled out with typographic means and an explicit reference.
        \end{itemize}
        \end{itemize}
    \item If you are incorporating any third-party material in the thesis, including works that you have authored/co-authored but for which you have transferred copyright, you must indicate that permission has been secured to use the material. For example: Fig.  2 reprinted with permission from the copyright holder, HolderName
\end{itemize}
Please, notice:  If you want to include other research merits, including published content and contributions which are not included in the Thesis, you should do that in the next page.

If no material from published or submitted contributions is included in this thesis, do not include this page.

%----------
%	OTHER RESEARCH MERITS
%----------	
\chapter*{Other research merits}
\thispagestyle{empty}
Include a list of research merits other than the published articles or other contributions in the Published Content and Contributions section.

If you do not wish to single out any other research merits, do not include this page.

%----------
%	TOC
%----------	

%--
% TOC
%-
\tableofcontents
\thispagestyle{fancy}

%--
% List of figures. If they are not included, comment the following lines
%-
\listoffigures
\thispagestyle{fancy}

%--
% List of tables. If they are not included, comment the following lines
%-
\listoftables
\thispagestyle{fancy}

%----------
%	THESIS
%----------	
\clearpage
\pagenumbering{arabic} % % numbering with Arabic numerals for the rest of the document.	

\chapter{Introduction}

% Start writing here----------------------------------------------------


%----------
%	Bibliography
%----------	

\clearpage
\addcontentsline{toc}{chapter}{Bibliography}

\printbibliography



%----------
%	Appendix
%----------	

% If your work includes Appendix, you can uncomment the following lines
%\chapter* {Appendix x}
%\pagenumbering{gobble} % Appendix pages are not numbered



\end{document}